Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-12 paper/main.tex

    Polar-orbiting satellites (Fig.~\ref{satellites}) are located in an orbital plane that is nearly 90 degrees inclined to the equatorial 
    plane. This tilt allows the satellite to perceive the entire earth, including polar regions, to observe locations that are difficult 
    to reach from the ground. Many polar-orbiting satellites are considered sun-synchronous, which means that the satellite passes through 
    the same position at the same solar time in each cycle. The polar orbit can be ascending or descending. In an ascending orbit, the satellite 
    moves from south to north as it passes the equator. In descending orbit, the satellite moves from north to south..

@@

    Low Earth Orbit (LEO) is an orbit relatively close to the surface of the earth. It is usually located at an altitude of fewer than 
    2000 kilometers, but it may be as low as 400 kilometers above the earth. Compared to other orbits, it is low, but still far from the 
    surface of the earth \cite{earthdata28:online}.It is the most commonly used orbit for satellite imaging because it is possible to take 
    higher resolution images close to the surface. It is also the orbit used by the International Space Station (ISS) because it is easier 
    for astronauts to travel to and from it at shorter distances. The satellite in this orbit travels at a speed of about 7.8 kilometers per 
    second; at this speed, it takes about 90 minutes for the satellite to orbit the earth, which means that the International Space Station 
    orbits the earth about 16 times a day \cite{ESAkerne12:online}.

@@

@@

    The orbit of a geostationary satellite can only be achieved at an altitude very close to 35,786 kilometers, and the satellite can 
    be fixed at one longitude of the equator. There are hundreds of communication satellites and several weather satellites in such orbits.

@@

\paragraph{Electromagnetic Spectrum}

>>>>

Polar-orbiting satellites (Fig.~\ref{satellites}) are located in an orbital plane that is nearly 90 degrees inclined to the equatorial 
plane. This tilt allows the satellite to perceive the entire earth, including polar regions, to observe locations that are difficult 
to reach from the ground. Many polar-orbiting satellites are considered sun-synchronous, which means that the satellite passes through 
the same position at the same solar time in each cycle. The polar orbit can be ascending or descending. In an ascending orbit, the satellite 
moves from south to north as it passes the equator. In descending orbit, the satellite moves from north to south.

@@

Low Earth Orbit (LEO) (Fig.~\ref{LEO})is an orbit relatively close to the surface of the earth. It is usually located at an altitude of fewer than 
2000 kilometers, but it may be as low as 400 kilometers above the earth. Compared to other orbits, it is low, but still far from the 
surface of the earth \cite{earthdata28:online}.It is the most commonly used orbit for satellite imaging because it is possible to take 
higher resolution images close to the surface. It is also the orbit used by the International Space Station (ISS) because it is easier 
for astronauts to travel to and from it at shorter distances. The satellite in this orbit travels at a speed of about 7.8 kilometers per 
second; at this speed, it takes about 90 minutes for the satellite to orbit the earth, which means that the International Space Station 
orbits the earth about 16 times a day \cite{ESAkerne12:online}.

@@

\\

@@

The orbit of a geostationary satellite (Fig.~\ref{Geostationary}) can only be achieved at an altitude very close to 35,786 kilometers, and the satellite can 
be fixed at one longitude of the equator. There are hundreds of communication satellites and several weather satellites in such orbits.

@@

\\

\paragraph{Electromagnetic Spectrum} 
The electromagnetic spectrum (Fig.~\ref{Spectrum})is a graph of electronic signals distributed according to frequency or wavelength \cite{electrom75:online}. Although all electromagnetic waves travel at the speed of light in vacuum, they have a wide range of frequencies, wavelengths, and photon energies. The entire electromagnetic spectrum is divided into radio waves, infrared radiation, visible light, ultraviolet radiation, X-rays, and gamma rays, but people are far away in gamma rays, so we will not discuss them. Due to the different emission, transmission and absorption of different waves, they have different practicability and practical range.
